Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-21 checking-executions.tex
modify

The following lemma states the correctness of $\textit{Check-PQ-Seq}$ (the proof can be found in Appendix~\ref{}).

>>>>

The following lemma states the correctness of $\textit{Check-PQ-Seq}$ (the proof can be found in Appendix~\ref{sec:appendix definition of seqPQ and proof of Lemma EQP rules and semantics}).
